%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = thesis.tex

\chapter{Abstract}

\paragraph{} Communication networks, whether traditional computer networks or hardware interconnects such as PCIe, serve as the backbone for disaggregated computing. 
Despite their differences in scale and implementation, both facilitate data exchange and are vulnerable to side-channel attacks that can cause unintended information leakage. 
We explore side-channel security across the two domains of internet networks and hardware interconnects, drawing parallels between them. 

We first focus on a scalable solution that can mitigate side-channel attacks in internet-like networks while providing the user with the facility to customise their own trade-offs between the side-channel mitigation guarantees, bandwidth overhead, and latency overhead.

The second part draws a parallel between existing network side-channel attacks and explores whether similar attacks can occur on modern PCIe interconnects.
By analysing commonalities in attack surfaces, this work provides a unified perspective on securing communication networks against side-channel threats.

The findings contribute to the broader goal of designing more resilient and secure communication mechanisms.

\endinput

The first part of this research focuses on mitigating side-channel attacks in traditional networks, proposing defences that minimise information leakage while preserving performance. 

The second part examines interconnects like PCIe, identifying side-channel vulnerabilities and developing detection mechanisms. 