%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = thesis.tex

\chapter{Acknowledgments}

I would like to express my deepest gratitude to my advisor, Prof. Aastha Mehta, whose unwavering support, invaluable guidance, and expertise have been instrumental in shaping this dissertation. 
Her dedication to mentoring, insightful feedback, and commitment to pushing the boundaries of my knowledge have been the driving forces behind this research endeavour. 
I would also like to thank my thesis committee, Margo Seltzer and Nguyen Phong Hoang, for their valuable feedback and guidance. 
Their insights have strengthened this work.

I would like to convey my sincerest appreciation to my collaborators, Amir Sabzi, Satvik Vemuganti, Arun Balamurali and Lucas Qin, whose tireless efforts have been indispensable throughout this project.

I would like to express my sincere gratitude to all members of the Systopia lab for their valuable ideas, discussions, and support throughout this work. 
The collaborative environment and shared knowledge have significantly contributed to the progress of this research.
I especially thank Joel Nider, Yayu Wang, Kjell Dankert, Sid Agrawal, Shaurya Patel and Reto Achermann for helping me with my various queries throughout my projects.
Their insights have been instrumental in refining concepts and overcoming challenges. 


\begin{comment}

I extend my heartfelt gratitude to Prof. Margo Seltzer for her invaluable contributions as a committee member for this dissertation.
Her extensive knowledge and keen insights have greatly enriched the depth and quality of this work.

\end{comment}
